Introducing ICBe: Supplementary Information

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_rmd.Rmd
win update

Significance Statement: Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

@@

litreview_ft_pnas   %>% 
    #flextable::flextable_to_rmd()
    save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

>>>>

Significance Statement {.unnumbered}
========================================

Countries routinely face crises that risk escalating into full scale war but we do not have systematic measurements of the progression of past crises and what moves and counter moves led to or helped avoid war. Instead policy makers typically rely on one or two historical analogies, chosen through ad hoc selection criteria, and described in unsystematic terms. This paper introduces a new scientific approach to measuring the step by step moves of international crises over the last hundred years, combining subject expertise with state of the art natural language processing and machine learning methods. It serves as a guide for constructing and evaluating large scale measurement collection in the social sciences.

@@

# Uncomment for snapshot
# litreview_ft_pnas %>% 
#     #flextable::flextable_to_rmd()
#     save_as_image(path=here::here("replication_paper", "pnas_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_rmd.tex
win update

@@

{[}1{]}
``/home/tlscherer/Desktop/ICBEdataset/replication\_paper/pnas\_draft/litreview\_ft.png''

>>>>

\hypertarget{significance-statement}{%
\section*{Significance Statement}\label{significance-statement}}
\addcontentsline{toc}{section}{Significance Statement}

Countries routinely face crises that risk escalating into full scale war
but we do not have systematic measurements of the progression of past
crises and what moves and counter moves led to or helped avoid war.
Instead policy makers typically rely on one or two historical analogies,
chosen through ad hoc selection criteria, and described in unsystematic
terms. This paper introduces a new scientific approach to measuring the
step by step moves of international crises over the last hundred years,
combining subject expertise with state of the art natural language
processing and machine learning methods. It serves as a guide for
constructing and evaluating large scale measurement collection in the
social sciences.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

@@

### 2022-08-24 replication_paper/political_analysis_draft/ICBe_pnas_submission_tex.tex
win update

\begin{figure*}
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
\end{figure*}

@@

\begin{figure*}
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure*}

@@

\begin{sidewaysfigure*}
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
\end{sidewaysfigure*}

@@

\begin{figure*}
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable. }
\end{figure*}

@@

\begin{figure*}
\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
\centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
\textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
\end{figure*}

>>>>

% \begin{figure*}
% \caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
% \centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
% \end{figure*}

\begin{figure*}
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.pdf"}}
\end{figure*}

@@

% \begin{figure*}
% \caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
% \centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.png}}
% \textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
% \end{figure*}

\begin{figure*}
\caption{Measuring Recall with Synthetic Historical Narratives \label{fig:case_study_cuban_recall}}
\centering{\includegraphics[height=18cm]{./recall_cuban_and_crimea_andcounts.eps}}
\textit{Notes: Synthetic narratives combine several thousand accounts of each crisis into a single timeline of events, taking only those mentioned in at least 5 or more documents. Checkmarks represent whether that event could be hand matched to any detail in the ICB corpus, ICBe dataset, or any of the other event datasets.}
\end{figure*}

@@

% \begin{sidewaysfigure*}
% \caption{Crisis Maps  \label{fig:p_precision_combined}}
% \centering{\includegraphics[width=22cm]{./p_precision_combined.png}}
% \end{sidewaysfigure*}

\begin{sidewaysfigure*}
\caption{Crisis Maps  \label{fig:p_precision_combined}}
\centering{\includegraphics[width=22cm]{./p_precision_combined.eps}}
\end{sidewaysfigure*}

@@

% \begin{figure*}
% \caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
% \centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.png}}
% \textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable. }
% \end{figure*}

\begin{figure*}
\caption{ICBe event codings in comparison to Semantic Embeddings from source sentences\label{fig:semantic_embeddings}}
\centering{\includegraphics[width=17cm]{./p_semantic_embeddings_dendro.pdf}}
\textit{Notes: Dots represent individual ICB narrative sentences, as embeded by the Paraphrase-MPNET-base-v2 large language model and flattened into two dimensions with UMAP. Text labels reflect individual leaves of the ICBe ontology, and colors represent intermediate branches of the ontology. Label placement is the median of all of the sentences that tag was applied to by the coders. The dendrogram shows hiearchical clustering of the tags. If ICBe precision is high, the sentences tags were applied to ought to say similar things, and the intended shape of the ontology ought to be visually recognizable. }
\end{figure*}

@@

% \begin{figure*}
% \caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
% \centering{\includegraphics[width=17cm]{./p_precision_icews.png}}
% \textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
% \end{figure*}

\begin{figure*}
\caption{ ICEWs Events by Day by Type during the Crimea-Donbas Crisis \label{fig:p_precision_icews}}
\centering{\includegraphics[width=17cm]{./p_precision_icews.pdf}}
\textit{Notes:Unit of analysis is the Dyad-Day. Edges <-> indicates undirected dyad and -> indicates directed dyad. Top 10 most active dyads per category shown. Red text shows events from the synthetic narrative relative to that event category. Blue bars indicate an event recorded by ICEWs for that dyad on that day. }
\end{figure*}

### 2022-08-24 replication_paper/political_analysis_draft/appendix.Rmd
win update

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft8.png"), zoom=1)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision1.png"), zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision2.png"), zoom=1) #

@@

ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision3.png"), zoom=1) #

@@

ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision4.png"), zoom=1) #

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_mids_metro_plot_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icews_plot_lv0_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
p_196_phoenix <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_196_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_196.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

@@

save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_196_combined.png'),
          p_196_combined, base_height = 12, base_width = 20)
#I'm just going to rotate on disk and load it as a normal figure
#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_196.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_471.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_471_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_penta_471.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_penta_471.Rds')
subtitle="Terrier Dyadic Events"
caption=paste0("Data: Terrier (Grant et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_penta_471.Rds')
p_471_icews <- readRDS(save_file)

@@

save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_471_combined.png'),
          p_471_combined, base_height = 12, base_width = 25)
}

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_phoenix_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_terrier_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "arxiv_draft", "p_icews_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

>>>>

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "pnas_draft", "crisis_text_counts_ft8.png"), zoom=1)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision1.png"), zoom=1) #

@@

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision2.png"), zoom=1) #

@@

ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision3.png"), zoom=1) #

@@

ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "pnas_draft", "ft_sample_precision_precision4.png"), zoom=1) #

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/pnas_draft/p_mids_metro_plot_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_phoenix_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_terrier_plot_lv0_",thiscrisis,".Rds")

@@

    print(thiscrisis)
    plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
    save_file_penta <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_penta_",thiscrisis,".Rds")
    save_file_lv0 <- paste0(here::here(), "/replication_paper/pnas_draft/p_icews_plot_lv0_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
p_196_phoenix <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  )

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_196_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_196.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_196_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

@@

save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_196_combined.png'),
          p_196_combined, base_height = 12, base_width = 20)
#I'm just going to rotate on disk and load it as a normal figure
#\begin{sidewaysfigure}[H] #can't trust sideways plots either so have to rate the image
}
```

@@

if(fromscratch){
  p_phoenix_plot_lv0_196 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_196.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_196.png'),
            p_phoenix_plot_lv0_196 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

## MIDs
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_471.Rds') 
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="Dyadic Militarized Interstate Disputes (MIDs)"
caption=paste0("Source: CrisisEvents.org (Douglass et al. 2021)
                Data: Dyadic Militarized Interstate Disputes (MIDs) (Maoz et al. 2019)
             ", p_metro_plot$labels$caption
             ) #tag original to bottom
p_471_mids <- p_metro_plot +
           theme(plot.margin=unit(c(0,0,0,0),"in")) +
  labs(
    #title = plot_title ,
    #subtitle = subtitle ,
    #caption = caption
  ) 
#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_mids_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

## Phoenix Crisis Map
#ICBe  196
library(ggplot2)
save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_penta_471.Rds')
subtitle="Phoenix Dyadic Events"
caption=paste0("Data: Cline Center Historical Phoenix Event Data (Althaus et al. 2017)
             ", p_metro_plot$labels$caption) #tag original to bottom

p_471_phoenix <- readRDS(save_file) +
    labs(
      #title = plot_title ,
      #subtitle = subtitle ,
      #caption = caption
    )
#ggsave(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_metro_plot_196.png'),
#       plot = p_metro_plot ,
#       width=12, height=14)

save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_penta_471.Rds')
subtitle="Terrier Dyadic Events"
caption=paste0("Data: Terrier (Grant et al. 2021)
             ", p_metro_plot$labels$caption) #tag original to bottom

@@

save_file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_penta_471.Rds')
p_471_icews <- readRDS(save_file)

@@

save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_471_combined.png'),
          p_471_combined, base_height = 12, base_width = 25)
}

@@

if(fromscratch){
  p_phoenix_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_phoenix_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_phoenix_plot_lv0_471.png'),
            p_phoenix_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_terrier_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_terrier_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_terrier_plot_lv0_471.png'),
            p_terrier_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```

@@

if(fromscratch){
  p_icews_plot_lv0_471 <- readRDS(here::here("replication_paper", "pnas_draft", "p_icews_plot_lv0_471.Rds"))
  save_plot(file=paste0(here::here(), '/replication_paper/pnas_draft/p_icews_plot_lv0_471.png'),
            p_icews_plot_lv0_471 + theme(legend.position="none") + ylab(''), base_height = 15, base_width = 20, limitsize = FALSE)
}
```
